The two models described in chapter 3 have very distinct features, from the grouping of the passengers according to their priority level to the order of seats being occupied as passengers come inside the airplane. In order to check which of the two has a more efficient boarding system, several statistics were computed at the end of each model's run time.

\indent\newline
First off, the total boarding time. This was considered as the time between the first passenger starting to board the plane and the last passenger sitting down, and it was measured with the help of TimeMeasurementStart component, a variable called "timeBoardStarted" that stores the time the first passenger showed their documentation and a function that keeps computing the difference between the present and that stored time, until all passengers are seated.
However, it is also important to understand why exactly a certain model’s boarding system finishes quicker. So additionally, four other performance metrics were focused on analyzing four different sections of the models: a) the pre-boarding time; b) the time prior to a passenger showing their documentation; c) the time related to passengers storing their luggage; d) the time it takes for passengers to sit down in their respective seats. 

\indent\newline
The time differences per passenger were obtained through placing TimeMeasurement components before or after specific blocks and were graphically displayed in Histograms and also Line Plots, which required storing them in data sets. Pie charts were also included in the Statistics window, with a different purpose in mind: by comparing the total number of times any passenger sits down or gets up from their seat, it is possible to know how inconvenient seat interference really is. Bins being full is another great inconvenience for passengers with luggage, which the second pie chart highlights, by counting the number of passengers that store their bags in a bin other than the one above their seat. Both pie charts’ inputs came from variables whose value got incremented every time a passenger entered blocks such as "pedGoToOtherBin" or "pedWaitOnSeat", for example.
